---
title: "Assignment 1"
author: "Molly Richard"
date: "29-Aug-2019"
output:
  html_document:
    df_print: paged
  html_notebook: default
  fig_caption: yes
  toc: yes
  pdf_document: default
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)
library(leaflet)

SMR <- read_csv("Master_Database_SMR only .csv")
```
### Introduction
Data were collected on cottonmouth snakes, *Agkistrodon piscivorus*, to assess a potential relationship between an individual's metabolic phenotype and the amount of corticosterone (CORT) produced when stress. The following figures and anaylsis are preliminary results assess the potential for sex or shedding state to impact the metabolic phenotype, and for the potential impact of cloacal temperature on the length of time to collect a blood sample for the CORT anaysis. 


### Standard Metabolic Rate Graph
```{r SMR graph}
ggplot(SMR, aes(x= Mass , y= Average_MR , shape=Sex, lty = Sex))+
  geom_point(aes(size = 2))+
  geom_smooth(method=(lm), se= FALSE)+
  xlab("Body Mass (g)") + ylab("Oxygen Consumption (mL O2 hour-1)")+
  theme_bw(base_size = 10)

```
<span> **Figure 1.** Shows the relationship between mass and standard metabolic rate in male and female cottonmouths, <em>Agkistrodon piscivorus</em>.</span>


### Energic Costs of Shedding
```{r Energic costs of shedding}
ggplot(SMR, aes(x= Mass , y= Average_MR, shape=Shedding, lty = Shedding))+
  geom_point(aes(size = 2))+
  geom_smooth(method=(lm), se = FALSE)+
  xlab("Body Mass (g)") + ylab("Oxygen Consumption (mL O2 hour-1)")+
  theme_bw(base_size = 10)
```
<span> **Figure 2.** Depicts that energetic costs of shedding in individual cottonmouths. </span>

### Statistical Analysis for SMR
An ancova was used to determine there is no significant difference between shedding and non-shedding individual's metabolic rate when accounting for mass (p=0.142, r<sup>2</sup>=0.6757, F=27.04, df=2,23). Mass of an individual was signifactant (p=3.89e-07, r<sup>2</sup>=0.6757, F=27.04, df=2,23).
```{r Analysis}
Shed_SMR <- lm(Average_MR ~ Mass + Shedding, data = SMR)
Shed_anova <- anova(Shed_SMR)
summary(Shed_SMR)
```
 
### Relationship between Blood Draw Speed and Temperature
```{r Base time and temp relationship}
ggplot(SMR, aes(x= Basetime , y= BaseTemp))+
  geom_point(aes(size = 2))+
  geom_smooth(method=(lm), se= FALSE)+
  xlab("Base Time (minutes)") + ylab("Base Temperature (C)")+
  theme_bw(base_size = 10)+
  theme(legend.position = "none")
```
**Figure 3** shows the Base Time which is the time to draw a blood sample after capture, and the associated temperature at the time collection. 

### Statistical Summary for Blood Draw Speed and Temperature
The statistical summary below shows that there is no significant relationship between the time to blood after capture and the cloacal temperature at the time of blood aquisition (p=0.52, r<sup>2</sup>=-0.023, F=0.4273, df=1,24).
```{r Statistical analysis for Blood time and temp}
blood <- lm(BaseTemp ~ Basetime, data = SMR)
blood_anova <- anova(blood)
summary(blood)
```

### Summary of All Data Collected 
The summary below gives a snap shot of the first 15 rows of data used in the graphs depicted.

```{r Table 1}

kable(SMR[1:15, ], format = "pandoc", caption = '<strong>Table 1.</strong>  A knitr table depicting the first 15 rows of data found in the SMR dataset.')
```      

### Summary Tables for Data
Tables 2 and 3 depict summary data of the average metabolic rates and average blood draw time of all cottonmouths, and the standard deviations between individuals and between times. 
```{r Table 2}
SMRsummary <- summarise(group_by(SMR),
                      n=n(), 
                      mean=mean(Average_MR), 
                      sd=sd(Mass))
kable(SMRsummary, format = "pandoc", caption = '<strong>Table 2.</strong>  A summary table displaying the number of snakes captured, the average metabolic rate(mL0<sup>2</sup> hour<sup>-1</sup>), and standard deviation of mass(g).') 
```

```{r Table 3}
SMRsummary <- summarise(group_by(SMR),
                      n=n(), 
                      mean=mean(Basetime), 
                      sd=sd(Basetime))
kable(SMRsummary, format = "pandoc", caption = '<strong>Table 3.</strong>  Depicts the average time to draw blood and the standard deviation between draw times in minutes.') 
```
 
### Map of Capture Locations
This interactive map shows the capture location of the `r nrow(SMR)` snakes captured in 2019.

```{r Map of study area}
leaflet(data=SMR) %>%
    addTiles() %>%
      addMarkers(data = SMR, lat = ~Latitude, lng = ~Longitude)
```
